---
title: "BiocChallenges"
author:
- name: Kevin Rue-Albrecht
  affiliation: University of Oxford
  email: kevinrue67@gmail.com
package: BiocChallenges
output:
  BiocStyle::html_document
abstract: |
  Challenges for the Biocoductor community.
vignette: |
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Welcome

The goal of <i class="fab fa-github"></i> `r BiocStyle::Githubpkg("kevinrue/BiocChallenges")` is to host challenges contributed by and for the Bioconductor community.

```{r, include=FALSE}
library(BiocChallenges)
```

# Challenge difficulty

Each challenge is accompanied by an estimated difficulty.
The difficulty level can be one of:

```{r, echo=FALSE, results='asis'}
cat(sprintf("- `%s`", BiocChallenges::difficulty_levels), sep = "\n")
```

# Topics

Each challenge is tagged by a list of topic labels to facilitate categorization and discoverability.
Topic tags can be any combination of valid 
<a href="https://bioconductor.org/packages/release/BiocViews.html" target="_blank"><em><strong>biocViews</strong></em></a>
 and the following additional ones:

```{r, echo=FALSE, results='asis'}
cat(sprintf("- `%s`", head(BiocChallenges::topic_tags,3)), sep = "\n")
```

New topics can be submitted as [pull requests](https://github.com/kevinrue/BiocChallenges/pulls) editing the [topics.R](https://github.com/kevinrue/BiocChallenges/blob/main/R/topics.R) script.
